---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit README.Rmd. -->

```{r, echo = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "tools/README-"
)
```

# sageparenting: Mom and dad in your console.
> "I'll give you something to cry about." -- Dad, circa 1985

[![Project Status: Active - The project has reached a stable, usable state and is being actively developed.](http://www.repostatus.org/badges/latest/active.svg)](http://www.repostatus.org/#active)
[![CRAN_Release_Badge](http://www.r-pkg.org/badges/version-ago/sageparenting)](https://CRAN.R-project.org/package=sageparenting)
[![CRAN_Download_Badge](http://cranlogs.r-pkg.org/badges/sageparenting)](https://CRAN.R-project.org/package=sageparenting)




## Installing `sageparenting`

`sageparenting` is available on [GitHub](https://github.com/emilioxavier/sageparenting) and on [CRAN](https://cran.r-project.org/package=sageparenting). To install it:

```{r, eval=FALSE}
# The easiest way to get sageparenting is:
install.packages("sageparenting")

# Or get the development version from GitHub:
install.packages("devtools")
devtools::install_github("emilioxavier/sageparenting")
```


## How to use `sageparenting`

```{r}
library(sageparenting)
sage.parenting()
```



## Have a suggestion? Need help? Found a bug?

* Contact [Emilio](https://github.com/emilioxavier) at emilio.esposito@gmail.com
* Submit an [issue via GitHub](https://github.com/emilioxavier/sageparenting/issues)


## Code of conduct

Please note that this project is released with a [Contributor Code of Conduct](CONDUCT.md). By participating in this project you agree to abide by its terms.

## License

MIT © [Emilio Xavier Esposito](https://github.com/emilioxavier)
